### 2022-12-23 docs/src/_intro.qmd

### Data and Model

@@

```{julia}
n_epochs = 100
model = Chain(Dense(2,1))
mod = FluxModel(model)

generator = GenericGenerator()
```

@@

@@

@@

@@

The package was developed for a research project that investigates the dynamics of various counterfactual generators.

>>>>

Below we first generate some synthetic data for a binary classification task and instantiate an instance of `CounterfactualData`.

@@

We then define a simple model for the task and prepare it for use with `CounterfactualExplanations.jl`:

```{julia}
n_epochs = 100
model = Chain(Dense(2,1))
mod = FluxModel(model)
```

To generate algorithmic recourse, we will use a simple generic generator:

```{julia}
generator = GenericGenerator()
```

Finally we train our model on a subset of the data. The chart below shows the results.

@@

To model the dynamics of algorithmic recourse, we use simulations, in which we repeatedly select as subset of individuals from the non-target class, generate and implement recourse for all of them and finally retrain the model. To set this experiment up, we can use the code below:

@@

Finally, we just run the experiment using default parameter settings that specify the number of rounds, the proportion of individuals to select for recourse and related aspects:

@@

The chart below shows the data and predictions at the end of the simulation:

@@

The package was developed for a research project that investigates the dynamics of various counterfactual generators. You can find the details [here](https://github.com/pat-alt/endogenous-macrodynamics-in-algorithmic-recourse).
